Development of a Reinforcement Learning Enabled Cattle Tracker Prototype

### 2025-02-14 paper/main.tex
Add graphs for prototype results

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Canadian AI Latex Template    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt]{cai}

\begin{document}
% Editorial staff will replace the following values:
% 1. Conference Year
% 2. Issue number
% 3. Article DOI
\def\conferenceyear{2025}
\volumeheader{38}{0}%{00.000}
\begin{center}

@@

The reinforcement learning agent outperforms the baseline agent by increasing the number of messages sent to the cloud by 4.3\% while maintaining a higher average power level by avoiding excess transmission actions.

\subsection{Deploymnet Results}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{./figs/power_levels.png}
    \caption{Power consumption levels of the cattle tracker over time. Different colors represent different operational phases such as data transmission, storage, and idle states.}
    \label{fig:power_levels}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Canadian AI Latex Template    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt]{cai}
\captionsetup{font=small}
\begin{document}
% Editorial staff will replace the following values:
% 1. Conference Year
% 2. Issue number
% 3. Article DOI
\def\conferenceyear{2025}
\volumeheader{38}{0}%{00.000}
\begin{center}

@@

The reinforcement learning agent outperforms the baseline agent by increasing the number of messages sent to the cloud by 4.3\% while maintaining a higher average power level by avoiding excess transmission actions.
The trained agent performed on average 2.12 collection actions for every transmission action, compared to a 1:1 ratio for the baseline agent.

\subsection{Deployment Results}

The trained agent was deployed and evaluated on the prototype hardware in an indoor environment over a 9 day period with occasional manual charging to ensure continuous operation.
This test evaluated the long-term performance of the agent and hardware system and the results are shown in Figure~\ref{fig:prototype_result}.
The hardware did experience

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.48\textwidth}
      \centering
      \includegraphics[width=\linewidth]{figs/prototype_power_level.png}
      \caption{Prototype power level over a 9 day collection window}
      \label{fig:prototype_power}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
      \centering
      \includegraphics[width=\linewidth]{figs/battery_level_vs_collection_ratio.png}
      \caption{Learned agent strategies as a function of power levels}
      \label{fig:battery_vs_collection}
  \end{subfigure}
  \caption{Collected data from the prototype hardware highlighting a nonlinear power level discharge and the learned agent strategies.}
  \label{fig:prototype_result}
\end{figure}

Figure~\ref{fig:prototype_power} highlights the nonlinear discharge curve of the battery over the 9 day period. 
The discharge rate during sleeping is relatively constant and the nonlinearity is a result of the mapping function of voltage to remaining capacity.
This nonlinearity poses a challenge to the agent, since it increases the error in future reward and remaining capacity estimation at lower power levels.

@@
